\documentclass[a4paper]{moderncv}
\usepackage{lmodern}
\usepackage[scale=0.75]{geometry}
\moderncvtheme[green]{classic}

\firstname{Bernardo}
\familyname{Borges}
\title{Curriculum Vitae}

\email{bernborgess@ufmg.br}
\homepage{homepages.dcc.ufmg.br/\~bernardoborges}
\social[github]{bernborgess}
\social[linkedin]{bernborgess}

\recipient{Bernardo Borges}{}

\opening{Dear PROFESSOR,}
\closing{Best regards,}

\begin{document}

\makelettertitle
My name is Bernardo Borges, and I am writing to express my interest in pursuing a PhD opportunity at
UNIVERSITY under your esteemed guidance.
I have been working as a researcher under Professor \link[Haniel Barbosa]{https://hanielbarbosa.com/}
at Universidade Federal de Minas Gerais, Brazil, in my graduation in Computer Science.
I have been working in the field of Formal Methods applied to his research in Satisfiability Modulo
Theories, what prompted me to learn Lean 4 and use it to formalize proof steps to be used in the
\link[cvc5]{https://cvc5.github.io/} tool.
In general I am interested in Functional Programming, Type Theory and Verification, as well as logic.

Given your work related to Lean, I am motivated to explore the possibility of contributing and learning
from your research group. I would be grateful if you could provide information on any available PhD
positions within your group or any upcoming opportunities to collaborate.
Additionally, I would appreciate any guidance on the application process and requirements for
prospective PhD candidates.

Thank you very much for considering my inquiry. I look forward to the possibility of discussing
this further.

\makeletterclosing

\newpage

\maketitle
\section{Personal Details}
\cvitem{Birth}{2000/04/04, Patos de Minas - MG, Brazil}
\cvitem{Nationality}{Brazillian}

\section{Work Experience}
\cventry{2023-2024}{Research Assistant}{Universidade Federal de Minas Gerais}{}{}
{Research on Lean 4 and Theorem Proving}
\cventry{2021-2023}{Web and Mobile Developer}{iJunior - Junior Enterprise}{}{}
{Application development and engineering for real clients, from sales and conception to delivery and support.}

\section{Projects}
\cventry{2024}{Formalization of Cutting Planes Reasoning}{smite - UFMG}{Belo Horizonte}{}
{Lean 4 \link[library]{https://github.com/bernborgess/lean-cutting-planes/} to model the
    foundational concepts of \link[cutting planes calculus]{https://jakobnordstrom.se/docs/presentations/TalkVeriPB_Dagstuhl23.pdf},
    verifying the correctness of its rules.}

\section{Language Skills}
\cvlanguage{Portuguese}{Native}{Born and raised in Minas Gerais - Brazil}
\cvlanguage{English}{Fluent}{Engaged for 7 years in English Courses, reaching C1
    level and Contact with native speakers through exchange program contacts}
\cvlanguage{German}{Fluent}{ Attained both theoretical and practical language
    skills through AFS Exchange Program in NRW-Germany, active participation in conversation
    groups, and accomplishment of the B2 Certificate by OnSet.}

\section{Other Abilities and Interests}
\cvlistitem{Functional Programming}
\cvlistitem{Category Theory and Type Theory}
\cvlistitem{Verification and Formal Methods}
\cvlistitem{Programming Languages: Haskell, Lean 4, Rust, TypeScript, C++, C, Python}

\end{document}